---
title: "Exposure to Asylum Seekers"
author: '[Jochem Tolsma](https://www.jochemtolsma.nl) - Radboud University, the Netherlands'
bibliography: references.bib
date: "Last compiled on `r format(Sys.time(), '%B, %Y')`"
output: 
  html_document:
    toc:  true
    toc_float: true
    number_sections: false
    code_folding: show
    code_download: yes
---

```{r, globalsettings, echo=FALSE, warning=FALSE}
library(knitr)
opts_chunk$set(tidy.opts=list(width.cutoff=100),tidy=TRUE, warning = FALSE, message = FALSE,comment = "#>", cache=TRUE, class.source=c("test"), class.output=c("test2"))
options(width = 100)
rgl::setupKnitr()


colorize <- function(x, color) {
  if (knitr::is_latex_output()) {
    sprintf("\\textcolor{%s}{%s}", color, x)
  } else if (knitr::is_html_output()) {
    sprintf("<span style='color: %s;'>%s</span>", color, 
      x)
  } else x
}

```

```{r klippy, echo=FALSE, include=TRUE}
klippy::klippy(position = c('top', 'right'))
#klippy::klippy(color = 'darkred')
#klippy::klippy(tooltip_message = 'Click to copy', tooltip_success = 'Done')
```

```{css, echo=FALSE}
pre.test {
  max-height: 300px;
  overflow-y: auto;
  overflow-x: auto;
  margin: 0px;
}

pre.test2 {
  max-height: 300px;
  overflow-y: auto;
  overflow-x: auto;
  margin: 0px;
  background-color: white
}


h1, .h1, h2, .h2, h3, .h3 {
    margin-top: 24px;
}


```

----

This website is a replication package for the paper "Exposure to Asylum Seekers and Changing Support for the Radical Right: A Natural Experiment in the Netherlands" by @Tolsma2020. It contains R code to replicate all Tables in the manuscript. 

Use the top menu to navigate to the section of interest. The section replicates the **Main Tables** of the manuscript. 

To copy the code click the button in the upper right corner of the code-chunks. 


----

## Data
All data and scripts can be found on [Github](https://github.com/JochemTolsma/ExposureASC2020)

----

## Contact
Questions can be addressed to the first author of the corresponding article, [Jochem Tolsma](mailto:j.tolsma@ru.nl). 

----  

## Additional dataprep  

We start with a datafile in long format we obtained after performing our dataprep, see [here](data/evazc v22122017.dta).  

- We delete observations of respondents where respondents were not allowed to vote or did not give an answer.  
- We delete observations with missing values on zipcode information.  
- We delete respondents with only one observation.  
- We construct the dichotomous dependent variable.  
- We construct the multinomial dependent variable. 
- We decided to perform additional robustness checks and need to match more raw data on crisis ASC. 


```{r, results='hide', class.source=c("test")}
rm(list=ls())

library(haven)

dataset <- read_stata("data/evazc v22122017.dta")

#dependent variable.
#delete not allowed to vote
table(dataset$vote, useNA = "always")
sum(table(dataset$vote, useNA = "always"))
dataset <- dataset[dataset$vote!=16,]
dataset <- dataset[dataset$vote!=17,]
#add 'VNL' to other party
dataset$vote[dataset$vote==12] <- 18
#"1"="vvd", "2"="pvda", "3"="pvv", "4"="cda", "5"="sp"
#"6"="d66", "7"="gl", "8"="cu", "9"="sgp", "10"="dier"
#"11"="50plus", "12"="vnl","13="blanco","14"="dontknow","15="no vote", "18"="other"
#define dichotomous dependent variable
dataset$y_pvv <- ifelse(dataset$vote==3, 1, 0)
#define multinomial dependent variable
dataset$vote_rwsp <- NA
dataset$vote_rwsp[dataset$vote==2 | dataset$vote==6 | dataset$vote==7 | dataset$vote==8 | dataset$vote==10 | dataset$vote==11 | dataset$vote==12 | dataset$vote==18] <- 0 #other
dataset$vote_rwsp[dataset$vote==1 | dataset$vote==4 | dataset$vote==9] <- 1 # right-wing
dataset$vote_rwsp[dataset$vote==5] <- 2 # anti-establishment 
dataset$vote_rwsp[dataset$vote==13 | dataset$vote==14 | dataset$vote==15] <- 3 #demobilized
dataset$vote_rwsp[dataset$vote==3] <- 4
# 1: right-wing; 2: anti-establishment; 3: demobilized; 0: other; 4: PVV

#delete respondents with missing data on zipcode
sum(is.na(dataset$pc4))
dataset <- dataset[!is.na(dataset$pc4),]

#delete respondents with only one observation.
dataset$one <- 1 
test <- aggregate(dataset$one, by=list(dataset$PanelistIdQuestion), FUN=sum)
names(test) <- c("PanelistIdQuestion", "ncases")
dataset <- merge(dataset, test)
table(dataset$ncases)
dataset <- dataset[dataset$ncases!=1,]

#recode tijd/time variable
table(dataset$tijd, useNA = "always")
dataset$tijd <- dataset$tijd - 1

#capacity of ASC
#s1 is regular, s2=temporary, s3=crisis, s123=total
dataset$s1pc4 <- ifelse(dataset$tijd==0, dataset$s1cap_pc4t1rel,dataset$s1cap_pc4t2rel)
dataset$s2pc4 <- ifelse(dataset$tijd==0, dataset$s2cap_pc4t1rel,dataset$s2cap_pc4t2rel)
dataset$s3pc4 <- ifelse(dataset$tijd==0, dataset$s3cap_pc4t1rel,dataset$s3cap_pc4t2rel)
dataset$s123pc4 <- dataset$s1pc4 + dataset$s2pc4 + dataset$s3pc4

#compute variables for hybrid model: within individual means (between vars) and deviations from mean (within vars). 
test <- aggregate(dataset[,c("contactnw", "threat", "s123pc4", "s1pc4", "s2pc4", "s3pc4", "y_pvv", "vote_rwsp" )], by=list(dataset$PanelistIdQuestion), FUN=mean)
names(test) <- c("PanelistIdQuestion", "contactnw_mean", "threat_mean",    "s123pc4_mean" ,  "s1pc4_mean" ,    "s2pc4_mean" ,    "s3pc4_mean" ,    "y_pvv_mean", "vote_rwsp_mean")
dataset <- merge(dataset, test)
dataset$contactnw_afw = dataset$contactnw - dataset$contactnw_mean
dataset$threat_afw = dataset$threat - dataset$threat_mean
dataset$s123pc4_afw = dataset$s123pc4 - dataset$s123pc4_mean
dataset$s1pc4_afw = dataset$s1pc4 - dataset$s1pc4_mean
dataset$s2pc4_afw = dataset$s2pc4 - dataset$s2pc4_mean
dataset$s3pc4_afw = dataset$s3pc4 - dataset$s3pc4_mean

#create filter vars for analyses: fe is fixed effects, fem is fixed effects multinomial
dataset$sel_fe = (dataset$y_pvv != dataset$y_pvv_mean)
dataset$sel_fem = (dataset$vote_rwsp != dataset$vote_rwsp_mean)
dataset$sel_s123pc4 = (dataset$s123pc4 != dataset$s123pc4_mean)

#match additional data on crisis ASC
#these data have been added in a later phase 
duur <- read.csv2("data/Adressen alle AZCs_17022017.csv")
names(duur)
duur <- duur[,c("PC4", "Soort", "Cap_Gem", "Duur.tot.4.11")]
names(duur) <- c("pc4", "soort", "cap", "duur")
duur <- duur[duur$soort==3,]
sort(unique(duur$pc4[duur$cap>0]))

#we are multiplying length of stay with number of AS
duur$s3_altop <- duur$duur * duur$cap
duur2 <- aggregate(duur[,c("cap", "duur", "s3_altop")], by=list(duur$pc4), FUN=sum)
duur2
names(duur2)[1] <- c("pc4")

dataset <- merge(dataset, duur2, all.x=T)
dataset$duur[is.na(dataset$duur)] <- 0
dataset$s3_altop[is.na(dataset$s3_altop)] <- 0
dataset$cap[is.na(dataset$cap)] <- 0

#asylum seekers in crisis centers per 1000 inhabitants weighted by length of stay
dataset$s3_altop2 <- 1000 * dataset$s3_altop / (dataset$inw2014_pc4 * dataset$pauto2014_pc4)
dataset$cap2 <- 1000 * dataset$cap / (dataset$inw2014_pc4 * dataset$pauto2014_pc4)
dataset$s3_altop <- 1000 * dataset$s3_altop / dataset$inw2014_pc4
dataset$cap <- 1000 * dataset$cap / dataset$inw2014_pc4


```




---  



## Table 1 {.tabset .tabset-fade}

### Fixed effects sample  

```{r, results="hold"}
library(psych)
require(DT) 

dataset_sel <- dataset[dataset$sel_fe==1,]
#table(dataset_sel$y_pvv, dataset_sel$tijd)
prop.table(table(dataset_sel$y_pvv, dataset_sel$tijd), margin=2)

#describeBy(dataset_sel[,c("s123pc4", "s1pc4", "s2pc4", "s3pc4", "threat", "contactnw", "s123pc4_afw", "s1pc4_afw", "s2pc4_afw", "s3pc4_afw", "threat_afw", "contactnw_afw")], group=dataset_sel$tijd)


test <- describeBy(dataset_sel[,c("s123pc4", "s1pc4", "s2pc4", "s3pc4", "threat", "contactnw", "s123pc4_afw", "s1pc4_afw", "s2pc4_afw", "s3pc4_afw", "threat_afw", "contactnw_afw")], group=dataset_sel$tijd)
#kable(round(test[[1]],2), caption="Time 1")
```

```{r, echo=FALSE, results="asis"}
datatable(round(test[[1]],2), caption="Time 1")
```

```{r, echo=FALSE, results="asis"}
datatable(round(test[[2]],2), caption="Time 2")
```


* respondents in FE sample: `r length(unique(dataset_sel$PanelistIdQuestion))`  
* zipcodes in FE sample: `r length(unique(dataset_sel$pc4))`  
* respondents experiencing change in FE sample: `r length(unique(dataset_sel$PanelistIdQuestion[dataset_sel$s123pc4!=dataset_sel$s123pc4_mean]))`  
* zipcodes experiencing change in FE sample: `r length(unique(dataset_sel$pc4[dataset_sel$s123pc4!=dataset_sel$s123pc4_mean]))`

---  


### hybrid model sample

```{r, results="hold"}

table(dataset$y_pvv, dataset$tijd)
prop.table(table(dataset$y_pvv, dataset$tijd), margin=2)

describeBy(dataset[,c("s123pc4", "s1pc4", "s2pc4", "s3pc4", "threat", "contactnw", "s123pc4_afw", "s1pc4_afw", "s2pc4_afw", "s3pc4_afw", "threat_afw", "contactnw_afw")], group=dataset$tijd)


print("respondents in hybrid sample")
length(unique(dataset$PanelistIdQuestion))

print("zipcodes in FE sample")
length(unique(dataset$pc4))

print("respondents experiencing change in FE sample")
length(unique(dataset$PanelistIdQuestion[dataset$s123pc4!=dataset$s123pc4_mean]))

print("zipcodes experiencing change in FE sample")
length(unique(dataset$pc4[dataset$s123pc4!=dataset$s123pc4_mean]))

```
--- 

## Table 2 {.tabset .tabset-fade}

```{r, results="hide"}
require(survival)
ev_sel <- dataset_sel 
m1 <- clogit(y_pvv ~ s123pc4 + tijd + strata(PanelistIdQuestion), data=ev_sel)
summary(m1)

#via different estimation of fixed effects model (a first difference design)
#only select y_observation at timepoint 2
ev_sel2 <- ev_sel[ev_sel$tijd==1,]
#need to multiply _afw with 2 (thus becomes t2-t1, instead of t2 - mean(t2,t1)
ev_sel2$s123pc4_afw <- 2*ev_sel2$s123pc4_afw
ev_sel2$s1pc4_afw <- 2*ev_sel2$s1pc4_afw
ev_sel2$s2pc4_afw <- 2*ev_sel2$s2pc4_afw
ev_sel2$s3pc4_afw <- 2*ev_sel2$s3pc4_afw
ev_sel2$threat_afw <- 2*ev_sel2$threat_afw
ev_sel2$contactnw_afw <- 2*ev_sel2$contactnw_afw

m1_alt1 <- glm(y_pvv ~ s123pc4_afw , data=ev_sel2, family=binomial)
m1_alt2 <- glm(y_pvv ~ s1pc4_afw + s2pc4_afw + s3pc4_afw , data=ev_sel2, family=binomial)
m1_alt3 <- glm(y_pvv ~ s1pc4_afw + s2pc4_afw + s3pc4_afw + contactnw_afw + threat_afw , data=ev_sel2, family=binomial)

```

### model 1

```{r, echo=FALSE}
summary(m1_alt1)
```

---  

### model 2

```{r, echo=FALSE}
summary(m1_alt2)
```

---  


### model 3

```{r, echo=FALSE}
summary(m1_alt3)
```


---  


## Table 3 {.tabset .tabset-fade}

```{r, results="hide"}
require(sandwich)
require(lmtest)
ev <- dataset

##hybrid model 
#because we include ethnic density of NB and SES of NB need to remove missing values.

#sum(is.na(ev$pnwal2014_pc4))
ev_sel4 <- ev[!is.na(ev$pnwal2014_pc4),]
#lost 90 respondents

ev_sel4 <- ev_sel4[!(ev_sel4$woz2012_pc4==0),]
#lost 22 respondents
ev_sel4 <- ev_sel4[!is.na(ev_sel4$woz2012_pc4),]
#lost 3 respondents

#center variables! 
ev_sel4$age_c <- ev_sel4$age - mean(ev_sel4$age)
ev_sel4$educ_c <- ev_sel4$educ - mean(ev_sel4$educ)
ev_sel4$pnwal2014_pc4_c <- ev_sel4$pnwal2014_pc4 - mean(ev_sel4$pnwal2014_pc4)
ev_sel4$woz2012_pc4_c <- ev_sel4$woz2012_pc4 - mean(ev_sel4$woz2012_pc4)

#run models
m1h <- glm(y_pvv ~ tijd + s123pc4_afw + s123pc4_mean + gender + age_c + educ_c + pnwal2014_pc4_c + woz2012_pc4_c, data=ev_sel4, family=binomial)
m2h <- glm(y_pvv ~ tijd + s1pc4_afw + s2pc4_afw + s3pc4_afw + s1pc4_mean + s2pc4_mean + s3pc4_mean + gender + age_c + educ_c + pnwal2014_pc4_c + woz2012_pc4_c, data=ev_sel4, family=binomial)
m3h <- glm(y_pvv ~ tijd + s1pc4_afw + s2pc4_afw + s3pc4_afw + s1pc4_mean + s2pc4_mean + s3pc4_mean + threat_mean + contactnw_mean + gender + age_c + educ_c + pnwal2014_pc4_c + woz2012_pc4_c, data=ev_sel4, family=binomial)
m4h <- glm(y_pvv ~ tijd + s1pc4_afw*pnwal2014_pc4_c + s2pc4_afw*pnwal2014_pc4_c + s3pc4_afw*pnwal2014_pc4_c + s1pc4_mean + s2pc4_mean + s3pc4_mean + threat_mean + contactnw_mean + gender + age_c + educ_c + woz2012_pc4_c, data=ev_sel4, family=binomial)


# summary(m1h)
# summary(m2h)
# summary(m3h)
# 
# coeftest(m1h, vcov = vcovCL(m1h, cluster = ~ PanelistIdQuestion))
# coeftest(m2h, vcov = vcovCL(m2h, cluster = ~ PanelistIdQuestion))
# coeftest(m3h, vcov = vcovCL(m3h, cluster = ~ PanelistIdQuestion))
```

### model 1  
```{r, echo=FALSE}
round(coeftest(m1h, vcov = vcovCL(m1h, cluster = ~ PanelistIdQuestion)), 3)
```

---  

### model 2  
```{r, echo=FALSE}
round(coeftest(m2h, vcov = vcovCL(m2h, cluster = ~ PanelistIdQuestion)), 3) 
```

---  

### model 3  
```{r, echo=FALSE}
round(coeftest(m3h, vcov = vcovCL(m3h, cluster = ~ PanelistIdQuestion)), 3)
```


--- 

### Model 4: no interaction with ethnic density

```{r, echo=FALSE}
round(coeftest(m4h, vcov = vcovCL(m4h, cluster = ~ PanelistIdQuestion)), 3)
```

--- 


## Inflow asylum seekers not related to PVV support T1. {.tabset .tabset-fade}

In our manuscript we state the following: 

> Voters of neighbourhoods that would experience an inflow of asylum seekers did not differ with respect to radical right support from voters that would not experience an inflow of refugees: pre-crises support for the PVV for both the ‘treated’ and ‘untreated’ groups was approximately 17%.

### dichtomeous treatment variable (total exposure)
```{r, results='hold'}
#define treatment variable: whether there has been an increase in total asylum seekers.  
dataset$treatment <- ifelse(dataset$tijd==1, as.numeric(dataset$s123pc4_afw>0), as.numeric(dataset$s123pc4_afw<0))

#check if treatment is not correlated with pretreatment outcome
test <- table(dataset$treatment[dataset$tijd==0],dataset$y_pvv[dataset$tijd==0])
dimnames(test)[[1]] <- c("treatment NO", "treatment YES" )
dimnames(test)[[2]] <- c("PVV NO", "PVV YES" )
test
prop.table(test, margin=1)
test1 <- glm(y_pvv ~ treatment, family=binomial, data=dataset[dataset$tijd==0,])
summary(test1)

```
This is what we report in the manuscript.  

- No selective treatment!  
- Among both groups, PVV support just below 17%

---  


### continuous treatment variable (total exposure)

```{r, results='hold'}
#define treatment variable: whether there has been an increase in total asylum seekers.  
dataset$treatment_c <- ifelse(dataset$tijd==1, dataset$s123pc4_afw, - dataset$s123pc4_afw)

#check if treatment is not correlated with pretreatment outcome
summary(glm(y_pvv ~ treatment_c, family=binomial, data=dataset[dataset$tijd==0,]))

```
Conclusion: No selectivity in treatment with respect to pre-crisis PVV support

---  

### dichtomeous treatment variable (crisis exposure)
```{r, results='hold'}
#define treatment variable based on crisis ASC only: whether there has been an increase in crisis asylum seekers. 
dataset$treatment2 <- ifelse(dataset$tijd==1, as.numeric(dataset$s3pc4_afw>0), as.numeric(dataset$s3pc4_afw<0))
#check if treatment2 is not correlated with pretreatment outcome
test <- table(dataset$treatment2[dataset$tijd==0],dataset$y_pvv[dataset$tijd==0])
dimnames(test)[[1]] <- c("treatment NO", "treatment YES" )
dimnames(test)[[2]] <- c("PVV NO", "PVV YES" )
test
prop.table(test, margin=1)
test2 <- glm(y_pvv ~ treatment2, family=binomial, data=dataset[dataset$tijd==0,])
summary(test2)
```
Conclusion:  

- no selectivity

---  

### continuous treatment variable (crisis exposure)

```{r, results='hold'}
#define treatment variable based on crisis ASC only: whether there has been an increase in crisis asylum seekers. 
dataset$treatment2_c <- ifelse(dataset$tijd==1, dataset$s3pc4_afw, - dataset$s3pc4_afw)
summary(glm(y_pvv ~ treatment2_c, family=binomial, data=dataset[dataset$tijd==0,]))
#table(dataset$treatment2,dataset$treatment2_c)
#summary(dataset$s3pc4_afw[dataset$tijd==0])
#summary(dataset$treatment2_c[dataset$tijd==0])
```
Conclusion:  

- no selectivity

---  

## Note 3 in manuscript  

- In the manuscript we state that the treatment is not related to pretreatment PVV support.  
- In note 3 we state that treatment is not related to an increase in contact or threat. 

We first define a treatment variable: 1 (YES, increase in asylum seekers); 0 (NO, no increase in asylum seekers)

```{r}

#show that treatment is not related to changes in threat and contact in fixed effect sample. note 3 in revised manuscript. 
#only select y_observation at timepoint 2
ev_sel2 <- dataset_sel[dataset_sel$tijd==1,]
ev_sel2$treatment <- ev_sel2$s123pc4_afw>0
mean(ev_sel2$contactnw_afw)
by(ev_sel2$contactnw_afw, ev_sel2$treatment, function(x) sd(x))
with(ev_sel2, t.test(contactnw_afw~treatment))
#treated group decrease in contact. untreated group increase in contact. difference in difference is significant. 

mean(ev_sel2$threat_afw)
by(ev_sel2$threat_afw, ev_sel2$treatment, function(x) sd(x))
with(ev_sel2, t.test(threat_afw~treatment))
#treated group increase in threat. untreated (less) increase in threat. difference in difference is not significant. 

```

---  

